### 2016-09-27 domain_specific.tex
Skip circuit_plot doctest
Compactify some symbol defs in Physics section

\begin{verbatim}
>>> from sympy.physics.vector import ReferenceFrame
>>> A = ReferenceFrame('A')
>>> B = ReferenceFrame('B')
>>> C = ReferenceFrame('C')
>>> B.orient(A, 'body', (pi, pi/3, pi/4), 'zxz')
>>> C.orient(B, 'axis', (pi/2, B.x))
>>> v = 1*A.x + 2*B.z + 3*C.y
>>> v
A.x + 2*B.z + 3*C.y
>>> v.express(A)
A.x + 5*sqrt(3)/2*A.y + 5/2*A.z
\end{verbatim}

@@

Symbolic quantum operators and states may be defined, and one can perform
a full range of operations with them.
\begin{verbatim}
>>> from sympy.physics.quantum import Commutator, Dagger, Operator
>>> from sympy.physics.quantum import Ket, qapply
>>> A = Operator('A')
>>> B = Operator('B')
>>> C = Operator('C')
>>> D = Operator('D')
>>> a = Ket('a')
>>> comm = Commutator(A, B)
>>> comm
[A,B]
>>> qapply(Dagger(comm*a)).doit()
-<a|*(Dagger(A)*Dagger(B) - Dagger(B)*Dagger(A))
\end{verbatim}
Commutators can be expanded using common commutator identities:
\begin{verbatim}
>>> Commutator(C+B, A*D).expand(commutator=True)
-[A,B]*D - [A,C]*D + A*[B,D] + A*[C,D]
\end{verbatim}

@@

\begin{verbatim}
>>> from sympy.physics.quantum.qubit import Qubit
>>> from sympy.physics.quantum.gate import XGate
>>> q = Qubit('0101')
>>> q
|0101>
>>> X = XGate(1)
>>> qapply(X*q)
|0111>
\end{verbatim}
Qubit states can also be used in adjoint operations, tensor products, inner/outer
products:
\begin{verbatim}
>>> Dagger(q)
<0101|
>>> ip = Dagger(q)*q
>>> ip
<0101|0101>
>>> ip.doit()
1
\end{verbatim}
Quantum gates (unitary operators) can be applied to transform these states and
then classical measurements can be performed on the results:
\begin{verbatim}
>>> from sympy.physics.quantum.qubit import measure_all
>>> from sympy.physics.quantum.gate import H, X, Y, Z
>>> c = H(0)*H(1)*Qubit('00')
>>> c
H(0)*H(1)*|00>
>>> q = qapply(c)
>>> measure_all(q)
[(|00>, 1/4), (|01>, 1/4), (|10>, 1/4), (|11>, 1/4)]
\end{verbatim}
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.65]{images/circuitplot-qft}
\caption{The circuit diagram for a three-qubit quantum Fourier transform
generated by SymPy.}
\label{fig-circuitplot-qft}
\end{center}
\end{figure}
Lastly, the following example demonstrates creating a three-qubit quantum Fourier
transform, decomposing it into one- and two-qubit gates, and then generating a
circuit plot for the sequence of gates (see Figure~\ref{fig-circuitplot-qft}).
\begin{verbatim}
>>> from sympy.physics.quantum.qft import QFT
>>> from sympy.physics.quantum.circuitplot import circuit_plot
>>> fourier = QFT(0,3).decompose()
>>> fourier
SWAP(0,2)*H(0)*C((0),S(1))*H(1)*C((0),T(2))*C((1),S(2))*H(2)
>>> c = circuit_plot(fourier, nqubits=3)
\end{verbatim}

>>>>

\begin{verbatim}
>>> from sympy.physics.vector import ReferenceFrame
>>> A, B, C = symbols('A B C', cls=ReferenceFrame)
>>> B.orient(A, 'body', (pi, pi/3, pi/4), 'zxz')
>>> C.orient(B, 'axis', (pi/2, B.x))
>>> v = 1*A.x + 2*B.z + 3*C.y
>>> v
A.x + 2*B.z + 3*C.y
>>> v.express(A)
A.x + 5*sqrt(3)/2*A.y + 5/2*A.z
\end{verbatim}

@@

Symbolic quantum operators and states may be defined, and one can perform
a full range of operations with them.
\begin{verbatim}
>>> from sympy.physics.quantum import Commutator, Dagger, Operator
>>> from sympy.physics.quantum import Ket, qapply
>>> A, B, C, D = symbols('A B C D', cls=Operator)
>>> a = Ket('a')
>>> comm = Commutator(A, B)
>>> comm
[A,B]
>>> qapply(Dagger(comm*a)).doit()
-<a|*(Dagger(A)*Dagger(B) - Dagger(B)*Dagger(A))
\end{verbatim}
Commutators can be expanded using common commutator identities:
\begin{verbatim}
>>> Commutator(C+B, A*D).expand(commutator=True)
-[A,B]*D - [A,C]*D + A*[B,D] + A*[C,D]
\end{verbatim}

@@

\begin{verbatim}
>>> from sympy.physics.quantum.qubit import Qubit
>>> from sympy.physics.quantum.gate import XGate
>>> q = Qubit('0101')
>>> q
|0101>
>>> X = XGate(1)
>>> qapply(X*q)
|0111>
\end{verbatim}
Qubit states can also be used in adjoint operations, tensor products, inner/outer
products:
\begin{verbatim}
>>> Dagger(q)
<0101|
>>> ip = Dagger(q)*q
>>> ip
<0101|0101>
>>> ip.doit()
1
\end{verbatim}
Quantum gates (unitary operators) can be applied to transform these states and
then classical measurements can be performed on the results:
\begin{verbatim}
>>> from sympy.physics.quantum.qubit import measure_all
>>> from sympy.physics.quantum.gate import H, X, Y, Z
>>> c = H(0)*H(1)*Qubit('00')
>>> c
H(0)*H(1)*|00>
>>> q = qapply(c)
>>> measure_all(q)
[(|00>, 1/4), (|01>, 1/4), (|10>, 1/4), (|11>, 1/4)]
\end{verbatim}
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.65]{images/circuitplot-qft}
\caption{The circuit diagram for a three-qubit quantum Fourier transform
generated by SymPy.}
\label{fig-circuitplot-qft}
\end{center}
\end{figure}
Lastly, the following example demonstrates creating a three-qubit quantum Fourier
transform, decomposing it into one- and two-qubit gates, and then generating a
circuit plot for the sequence of gates (see Figure~\ref{fig-circuitplot-qft}).
% This depends on matplotlib. We want to make sure the rest of the paper
% doesn't depend on it, so skip.
% no-doctest
\begin{verbatim}
>>> from sympy.physics.quantum.qft import QFT
>>> from sympy.physics.quantum.circuitplot import circuit_plot
>>> fourier = QFT(0,3).decompose()
>>> fourier
SWAP(0,2)*H(0)*C((0),S(1))*H(1)*C((0),T(2))*C((1),S(2))*H(2)
>>> c = circuit_plot(fourier, nqubits=3)
\end{verbatim}
